---
title: "Alcohol vs Seat choice"
author: "Roxan Barakat"
date: "Spring 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The fancy notch box plot displays 3 different categories of people's seating (back, front, and middle). We can observe that people who're seated in the back has a median that differs, yet the people seating in the front and middle have more confidence in their median data. Therefore, we can make a hypothesis that people in the back have a higher average of consuming alcohol drinks than those who are seated in the middle and front. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
The numerical data shows that the average number of drinks for the people who are seated at the back is about 9 drinks, which is 3x the average number of drinks for people who are seated in the middle, and 9x the average number of people who are seated in the front.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The inferential test shows a small number of P-value with 0.000116, which means this is the probability of having no difference between the alcohol consumed between the 3 row (back, front, middle) options that's available for people to be seated at.

## Conclusions


